The Influence of Connectivity on Dung Beetle Communities

### 2025-07-09 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
updates

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\small{EEC MS Thesis Draft}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}
  - \setcounter{secnumdepth}{0} # removes numbering from sections and subsections
  - \usepackage{sectsty}\allsectionsfont{\raggedright}
  - \usepackage{sectsty}\sectionfont{\centering}{\normalfont} # center # headings
  - \usepackage{sectsty}\subsectionfont{\centering}{\normalfont} # center ## headings
  - \usepackage{sectsty}\subsubsectionfont{\bfseries} # center ## headings
  # - \usepackage{sectsty}\subsubsectionfont{\itshape} # no centering but italic subsu
  # - \usepackage{sectsty}\subsubsectionfont{\centering}{ital} # center ### headings
  # - \usepackage{sectsty}\sectionfont{\centering\color{darkmidnightblue}}

 # - doublespacing # manipulate line spacing 
# - \usepackage{parskip} # manipulate indents and spacing before/after paragra phs 
# - \usepackage{xcolor} # changes colors of text
# # http://latexcolor.com/ to choose colors
# # define the colors used above with rgb codes
# - \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
# - \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
# # to center to top level (#) headings (my name) and change color of font
# # more info # https://www.ctan.org/pkg/sectsty
# - \usepackage{sectsty}
# - \sectionfont{\centering\color{darkmidnightblue}}
# # to center to sub-sub-headings (###) and change color of font
# - \usepackage{sectsty} 
# - \subsectionfont{\centering\color{darkmidnightblue}}
# - \usepackage{sectsty} 
# - \subsubsectionfont{\raggedright\color{darkmidnightblue}}
# - \usepackage{wrapfig} 
# - \newcommand{\blandscape}{\begin{landscape}}
# - \newcommand{\elandscape}{\end{landscape}}
# - \usepackage[font=small,labelfont=bf]{caption} #Required for specifying captions to tables and figures
# - \usepackage{indentfirst}
# - \setlength\parindent{22pt} # uncomment if you want indented paragraphs
bibliography: ["eric-thesis.bib"]
output:
  bookdown::pdf_document2:
    toc: false
# output: bookdown::pdf_document2
  # pdf_document:
  #   includes:
  #     # in_header: style/preamble.tex
  #     template: null
  #     keep_tex: no
  #     extra_dependencies: ["float"]
      # number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

## INTRODUCTION

@@

## METHODS

### Study site

@@

## RESULTS

@@

## DISCUSSION

<!-- Paragraph 1: Overview: While there may indeed be effects of patch area and connectivity on dung beetle abundance on community composition, other (landscape-scale) drivers appear to be more important.  -->

@@

## REFERENCES

@@

## FIGURES & TABLES

@@

knitr::include_graphics("images/sp_abund.png")

>>>>

header-includes:
  - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \raggedbottom
  - \usepackage{fancyhdr}
  - \pagestyle{plain}
  - \fancyfoot[C]{\thepage}
  - \fancyhead[L]{}
  - \fancyhead[R]{\small{EEC MS Thesis Draft}}
  - \thispagestyle{fancy}
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
  - \usepackage{indentfirst}
  # - \usepackage{caption}
  # - \captionsetup[figure]{name={Figure 1-},labelsep=period}
  # - \captionsetup[table]{name={Table 1-},labelsep=period}
  - \renewenvironment{abstract}{}{} #suppress the abstract
  - \usepackage{setspace}
  - \setcounter{secnumdepth}{0} # removes numbering from sections and subsections
  - \usepackage{sectsty}\allsectionsfont{\raggedright}
  # - \usepackage{sectsty}\sectionfont{\centering}{\normalfont} # center # headings
  # - \usepackage{sectsty}\subsectionfont{\centering}{\normalfont} # center ## headings
  - \usepackage{sectsty}\subsubsectionfont{\bfseries} # center ## headings
  # - \usepackage{sectsty}\subsubsectionfont{\itshape} # no centering but italic subsu
  # - \usepackage{sectsty}\subsubsectionfont{\centering}{ital} # center ### headings
  # - \usepackage{sectsty}\sectionfont{\centering\color{darkmidnightblue}}

 # - doublespacing # manipulate line spacing 
# - \usepackage{parskip} # manipulate indents and spacing before/after paragra phs 
# - \usepackage{xcolor} # changes colors of text
# # http://latexcolor.com/ to choose colors
# # define the colors used above with rgb codes
# - \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
# - \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
# # to center to top level (#) headings (my name) and change color of font
# # more info # https://www.ctan.org/pkg/sectsty
# - \usepackage{sectsty}
# - \sectionfont{\centering\color{darkmidnightblue}}
# # to center to sub-sub-headings (###) and change color of font
# - \usepackage{sectsty} 
# - \subsectionfont{\centering\color{darkmidnightblue}}
# - \usepackage{sectsty} 
# - \subsubsectionfont{\raggedright\color{darkmidnightblue}}
# - \usepackage{wrapfig} 
# - \newcommand{\blandscape}{\begin{landscape}}
# - \newcommand{\elandscape}{\end{landscape}}
# - \usepackage[font=small,labelfont=bf]{caption} #Required for specifying captions to tables and figures
# - \usepackage{indentfirst}
# - \setlength\parindent{22pt} # uncomment if you want indented paragraphs
bibliography: ["eric-thesis.bib"]
output:
  bookdown::pdf_document2:
    # toc: false
    number_sections: true
    fig_caption: true

# output: bookdown::word_document2
# output: word_document
# output: html_document

# output: bookdown::pdf_document2
  # pdf_document:
  #   includes:
  #     # in_header: style/preamble.tex
  #     template: null
  #     keep_tex: no
  #     extra_dependencies: ["float"]
      # number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

@@

\begin{center} 
\textbf{Methods}
\end{center}
### Study site

@@

\begin{center} 
\textbf{Results}
\end{center}

@@

\begin{center} 
\textbf{Discussion}
\end{center}
<!-- Paragraph 1: Overview: While there may indeed be effects of patch area and connectivity on dung beetle abundance on community composition, other (landscape-scale) drivers appear to be more important.  -->

@@

\begin{center} 
\textbf{References}
\end{center}

@@

@@

knitr::include_graphics("images/total_abund.png")
